---
title: "NY NOAA Plots "
output: 
  html_document:
    toc: true
    toc_float: true
---

This page provides plotting examples of the NY NOAA dataset using plotly.

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

The data subset used in plots are records of 10 randomly selected stations in 2010.

```{r}
df =
  ny_noaa %>%
  separate(date, c("year", "month", "day"), sep = "-") %>%
  mutate(
    year = as.numeric(year),
    month = as.numeric(month),
    day = as.numeric(day),
    prcp = as.numeric(prcp)*0.1,
    tmax = as.numeric(tmax)*0.1,
    tmin = as.numeric(tmin)*0.1) %>%
  drop_na(tmin, tmax)  %>%
  filter(year==2010,
         id %in% c("USC00301752", "USC00300889", "USC00301787",
                   "USC00300961", "USC00302366", "USC00304791",
                   "USC00300023", "USC00301401", "USC00301095",
                   "USC00300732")
         ) %>%
  mutate(date = paste(month, day, sep = "/"))
```

##### Scatterplot

This plot shows the minimum and maximum temperature and percipitation in the first half of 2010.

```{r}
df %>%
  filter(month %in% c(1, 2, 3, 4, 5, 6)) %>% 
  mutate(text_label = str_c("Date:", date,  "\n Site ID:", id)) %>% 
  plot_ly(
    x = ~tmin, y = ~tmax, type = "scatter", mode = "markers",
    color = ~prcp, text = ~text_label, alpha = 0.5)
```

##### Boxplot

This plot shows the minimum year round minimum temperature in 2010 among different stations.

```{r}
df %>% 
  mutate(id = as.factor(id)) %>% 
  plot_ly(y = ~tmin, color = ~id, type = "box", colors = "viridis")
```


##### Barplot 

This plot shows distribution of snowing days in 2010 by station.
```{r}
df %>% 
  filter(snow>0) %>%
  group_by(id) %>%
  count(snow) %>%
  plot_ly(x = ~id, y = ~n, color = ~id, type = "bar", colors = "viridis")
```

